### 2021-02-20 paper.tex
Update todo
Add something to filter section.

\todo{konrad fills out the use cases from the book}
SNIK Graph supports the following use cases:

@@

\section*{Implementation and Setup}
Following the design goals, SNIK Graph is implemented in JavaScript (EcmaScript 2015) using the graph visualization library Cytoscape.js~\cite{cytoscape}.
SNIK Graph is freely available as open source software\footnote{\url{https://github.com/imise/snik-cytoscape.js}}.
As a client-side tool\footnotemark{}, SNIK Graph can be adapted for other knowledge bases and ontologies and published on any HTML web server by cloning the repository, installing the NPM dependencies and adapting the configuration file settings including the SPARQL endpoint URL.
\footnotetext{Aside from a SPARQL endpoint.}
An installation containing SNIK is published at \url{https://www.snik.eu/graph}.

\section*{Features}
\subsection*{Filters}

@@

\subsection*{Role Use}
\begin{figure}[h]
\begin{lstlisting}
SELECT DISTINCT ?inner ?middle ?outer ?outerx {
 <role> (rdfs:subClassOf|skos:closeMatch|^skos:closeMatch)* ?inner.
 ?inner meta:subTopClass meta:Role.
 OPTIONAL {
  ?inner ?p ?middle.
  ?middle meta:subTopClass meta:Function.
  OPTIONAL {
   ?middle ?q ?outer.
   ?outer meta:subTopClass meta:EntityType.
   OPTIONAL {?outer (skos:closeMatch|^skos:closeMatch|^rdfs:subClassOf)+ ?outerx.}
}}}
\end{lstlisting}
\caption{SPARQL query to generate the \emph{role use} visualization.}
\label{lst:roleuse}
\end{figure}
\vspace{-3pt}
A frequent question is, what a given role does and which information is needed for those functions represented by the entity types connected to those functions.
This question is visually answered by the \enquote{role use} feature, which arranges roles, functions and entity types in concentric circles, see \Cref{fig:classuse}:

@@

\section*{Approach}
%Due to its large size, visualizing all of SNIK at once  overplotting.
At the core of SNIK Graph is incremental exploration, which starts at one or more nodes and gradually expands them to related ones.

@@

Different presentation forms are suitable for different use cases and data sets.
% RDF browsers are well suited for ...

>>>>

\todo{thomas continues the use cases from the book (only list those that are supported)}
SNIK Graph supports the following use cases:

@@

\section*{Implementation and Setup}
Following the design goals, SNIK Graph is implemented in JavaScript (EcmaScript 2015) using the graph visualization library Cytoscape.js~\cite{cytoscape}.
SNIK Graph is freely available as open source software\footnote{\url{https://github.com/imise/snik-cytoscape.js}}.
As a client-side tool\footnotemark{}, SNIK Graph can be adapted for other knowledge bases and ontologies and published on any HTML web server by cloning the repository, installing the NPM dependencies and adapting the configuration file settings including the SPARQL endpoint URL.
\footnotetext{Aside from a SPARQL endpoint.}%
An installation containing SNIK is published at \url{https://www.snik.eu/graph}.

\section*{Features}
\subsection*{Filters}
Classes, instances and properties of SNIK can be hidden based on type, such as Role, and knowledge source (SPARQL graph).

@@

\subsection*{Role Use}
\todo{konrad an alle: was mache ich mit der sparql query? rausschmeissen, drin lassen oder umbauen?}
\begin{figure}[h]
\begin{lstlisting}
SELECT DISTINCT ?inner ?middle ?outer ?outerx {
 <role> (rdfs:subClassOf|skos:closeMatch|^skos:closeMatch)* ?inner.
 ?inner meta:subTopClass meta:Role.
 OPTIONAL {
  ?inner ?p ?middle.
  ?middle meta:subTopClass meta:Function.
  OPTIONAL {
   ?middle ?q ?outer.
   ?outer meta:subTopClass meta:EntityType.
   OPTIONAL {?outer (skos:closeMatch|^skos:closeMatch|^rdfs:subClassOf)+ ?outerx.}
}}}
\end{lstlisting}
\caption{SPARQL query to generate the \emph{role use} visualization.}
\label{lst:roleuse}
\end{figure}
\vspace{-3pt}
A frequent question is, what a given role does and which information is needed for those functions represented by the entity types connected to those functions.
This question is visually answered by the \enquote{role use} feature, which arranges roles, functions and entity types in concentric circles, see \Cref{fig:classuse}:

@@

%\section*{Approach}
%Due to its large size, visualizing all of SNIK at once  overplotting.
%At the core of SNIK Graph is incremental exploration, which starts at one or more nodes and gradually expands them to related ones.

@@

%Different presentation forms are suitable for different use cases and data sets.
\todo{conclusions}
% RDF browsers are well suited for ...
